---
title: \LaTeX Template
output:
  pdf_document:
    toc: false
    latex_engine: xelatex
    fig_caption: true
    includes:
      in_header:
      - "../Templates/Magazine-preamble.tex"
fontsize: 12pt
linestretch: 1
documentclass: book
pagestyle: plain
classoption:
- twoside
- openany
indent: true
editor_options:
  chunk_output_type: inline
always_allow_html: true
---
```{r, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  results = 'asis'
)

include_text <- function(textfile) {
  cat(readLines(here::here(textfile)))
}
```

\pagenumbering{gobble}
\InsertFullPicture{../Images/Magazine-cover.jpg}

\clearpage
\InsertFullPicture{../Images/Alice-in-Wonderland-page-2.png}
\clearpage
\pagenumbering{roman}

\vspace*{2in}
\HUGEST
\begin{center}
MaD HaTTeR Magazine
\end{center}
\vspace*{\fill}

\newpage 

\phantom{page}

\newpage


\vspace*{\fill}
\BIG{Dear readers,}\large
This is a demonstration of what the magazine template can look like.

\begin{spacing}{1.5}
Sincerely, \newline
Endocrinology ‘24 \newline
Mount Allison University
\end{spacing}
\normalsize
\vspace*{\fill}
\small
This magazine was typeset in RMarkdown and \LaTeX\ using a template developed by Christelinda Laureijs. Unless otherwise stated, all images were licensed for reuse and adaptation or released under a public domain license.
\normalsize


\clearpage



```{r}
include_text("Submissions/Alice-in-Wonderland.txt")
```


